---
title: "Decode CSV data for C3PO"
author: "Michael Corace"
date: "7/19/2022"
output: html_document
---

Libraries
```{r}
library(jsonlite)
library(tidyverse)
install.packages("readxl")
library(readxl)
library(dplyr)
library(stringr)
library(jsonlite)
```

First, let's see what we can extract from the provided data dictionary.
```{r}
dd_path <- '../input/DataDictionary.csv'

# read in the csv to a data frame
data_dictionary_df <- read.csv(dd_path)
```

This study provides an additional decoding file, a Code List.
Now we'll load in this file as well, and extract info we need from it.

```{r}
cl_path <- '../input/Codelist.csv'

# read in the csv to a data frame
codelist_df <- read.csv(cl_path)

```

This codelist has the coded variable ids and decoded names in the same field.
So now we separate those into different columns to be used more easily.

```{r}

codelist_df$label_name_list <- vector(mode="character",length = length(codelist_df$label_list))

for (i in 1:length(codelist_df$label_list)) {
  #print(codelist_df$label_list[i])
  label_name <- strsplit(codelist_df$label_list[i], "=")
  
  codelist_df$label_list[i] <- gsub('\"','',label_name[[1]][1])
  codelist_df$label_name_list[i] <- gsub('\\\\','', gsub('\"','',label_name[[1]][2]))
}

```

Now we read in each csv and decode the data

```{r}
special_vars <- c("zRaceM1","zRaceM2","zRaceM3","zRaceM4","zRaceM5","zRaceM98")


form_files_list <- list.files('../input/',pattern = 'unmapped')

for(form in form_files_list){
  form_raw <- read.table(paste0("../input/",form), head = TRUE, sep=",")
  
  for(v in colnames(form_raw)){
    if (v %in% data_dictionary_df$varname){
      #print(v)
      var_code_df <- data_dictionary_df[which(data_dictionary_df$varname == v),3:4]
      
      for (i in c(1:length(var_code_df$start))) {
        form_raw[v][form_raw[v] == var_code_df$start[i]] <- var_code_df$label[i]
        form_raw[v][is.na(form_raw[v])] <- ""
      }
      
    }else if(v %in% special_vars){
      for (variable in special_vars) {
        form_raw[variable][form_raw[variable] == 0] <- "No"
        form_raw[variable][form_raw[variable] == 1] <- "Yes"
      }
    }
  }
  
  
  write.csv(form_raw, paste0("../output/decoded_",form), row.names = F)
}
```