---
title: "Curate Metadata for C3PO"
author: "Michael Corace"
date: "7/6/2022"
output: html_document
---

Libraries
```{r}
library(jsonlite)
library(tidyverse)
install.packages("readxl")
library(readxl)
library(dplyr)
library(stringr)
library(jsonlite)
```
To-Do
******




First, let's see what we can extract from the provided data dictionary.
```{r}
dd_path <- '../input/DataDictionary.csv'

# read in the csv to a data frame
data_dictionary_df <- read.csv(dd_path)
```

This study provides an additional decoding file, a Code List.
Now we'll load in this file as well, and extract info we need from it.

```{r}
cl_path <- '../input/Codelist.csv'

# read in the csv to a data frame
codelist_df <- read.csv(cl_path)

```

This codelist has the coded variable ids and decoded names in the same field.
So now we separate those into different columns to be used more easily.

```{r}

codelist_df$label_name_list <- vector(mode="character",length = length(codelist_df$label_list))

for (i in 1:length(codelist_df$label_list)) {
  #print(codelist_df$label_list[i])
  label_name <- strsplit(codelist_df$label_list[i], "=")
  
  codelist_df$label_list[i] <- gsub('\"','',label_name[[1]][1])
  codelist_df$label_name_list[i] <- gsub('\\\\','', gsub('\"','',label_name[[1]][2]))
}

```


Build Variable Data Frame

```{r}

variable_df <- data.frame("form_name" = codelist_df$table_name,
                          "variable_id" = codelist_df$label_list,
                          "variable_name" = codelist_df$label_name_list,
                          "variable_type" = rep(NA, length(codelist_df$label_list)),
                          "variable_label_from_data_dictionary" = codelist_df$label_name_list,
                          "variable_label_from_data_file" = rep(NA, length(codelist_df$label_list)))
                          
special_vars <- c("zRaceM1","zRaceM2","zRaceM3","zRaceM4","zRaceM5","zRaceM98")
# Determine the type of each variable
for(i in c(1:length(variable_df$variable_id))){
  if(variable_df$variable_id[i] %in% data_dictionary_df$varname || variable_df$variable_id[i] %in% special_vars){
    variable_df$variable_type[i] <- "ENCODED VALUE"
  }else{
    variable_df$variable_type[i] <- "numeric"
  }
  # add in variable metadata label
  #variable_df$variable_metadata[i]$variable_label_from_data_dictionary <- variable_df$variable_name[i]
}

```


Check all form files for any additional variables not contained within the lists
This includes variables already on the list, but not associated with that specific form
```{r}
form_files_list <- list.files('../input/',pattern = 'unmapped')

for(form in form_files_list){
  vars <- colnames(read.table(paste0("../input/",form), head = TRUE, nrows=1, sep=",")[-1,])
  for(v in vars){
    if(!(v %in% variable_df$variable_id)){
      #print(v)
      #print(form)
      # this was used to catch the 3 variables not listed, since it is a small number I just added them in manually
    }else {
        form_num <- paste0("Form",str_match(form,"CONNECTS_(.*?)_unmapped\\.csv")[,2])

        if((v %in% variable_df$variable_id) && !(form_num %in% variable_df$form_name[which(variable_df$variable_id == v)] )){
          variable_df <- rbind(variable_df, data.frame("form_name" = form_num,
                                                       "variable_id" = v,
                                                       "variable_name" = variable_df$variable_name[which(variable_df$variable_id == v)][1],
                                                       "variable_type" = variable_df$variable_type[which(variable_df$variable_id == v)][1],
                                                        "variable_label_from_data_dictionary" = variable_df$variable_label_from_data_dictionary[which(variable_df$variable_id == v)][1],
                                                        "variable_label_from_data_file" = NA))
        }
    }
  }
}

# There are 3 variables found in a form that have no description in the codelist or data dictionary
# Upon review they are all from the same form, so I will just add them manually here

variable_df <- rbind(variable_df, data.frame("form_name" = c("Form104","Form104","Form104"),
                                                       "variable_id" = c("zCRFID","socname","ptname"),
                                                       "variable_name" = c("zCRFID","socname","ptname"),
                                                       "variable_type" = c("numeric","string","string"),
                                                        "variable_label_from_data_dictionary" = c(NA,NA,NA),
                                                        "variable_label_from_data_file" = c("zCRFID","socname","ptname")))

```


#### CONNECTS CDE DOMAINS ####
Read in and save the CONNECTS CDE Domains
These are Common Data Elements defined in the CONNECTS CDE MANUAL found at: https://nhlbi-connects.org/common_data_elements

```{r}

# CDE_list <- c("DM","MH","RSK","ORG","SYM","AE","CM","VS","LB","COVID","VAC","DS","DS","INT","HO")

# Ensure each CDE Domain exists in the study, and save them in a data frame
# for(CDE in CDE_list){
#  if(file.exists(paste0("../input/",CDE,".csv"))){
#    tmp_df <- read.csv(paste0("../input/",CDE,".csv"), check.names = F)
#    assign(paste0(CDE,"_df"),tmp_df)
#  }
#}


```
#


## Create JSON file

Start with variable metadata
```{r}
#var_df <- variable_df %>% unique() 

for(ind in 1:nrow(variable_df)){
  meta_df <- variable_df[which(variable_df$variable_id == variable_df$variable_id[ind]),5:6]
  variable_df[ind, 'variable_metadata'] [[1]] <- list(meta_df[1,])
}
variable_df<- variable_df[,c(1:4,7)]
```

Group variables into forms
```{r}
form_df <- variable_df %>% select(form_name) %>% unique()

for(ind in 1:nrow(form_df)){
  f_df <- variable_df[which(variable_df$form_name == form_df$form_name[ind]),c(2:5)]
  form_df[ind,'variable'] [[1]] <-list(f_df)
}
```



Group forms into study
```{r}
study_df <- data.frame('study' = 'C3PO', 
                       'study_name' = 'Convalescent Plasma in Outpatients With COVID-19 (C3PO)',
                       'study_phs_number' = 'phs002752', 
                       'study_url' = 'https://www.ncbi.nlm.nih.gov/projects/gap/cgi-bin/study.cgi?study_id=phs002752.v1.p1')

study_df[1, 'form'][[1]] <- list(form_df)



```

Write JSON

```{r}
my_json <- toJSON(study_df, pretty=FALSE)
json_string <- as.character(my_json) # Convert to character/string
fileConn <- file("../output/c3po_metadata.json")
writeLines(json_string, fileConn)
close(fileConn)
# This works for writing a JSON file without the escape characters
```

