---
title: "BABY HUG Curation"
output: html_document
---

Libraries
```{r}
library(tidyverse)
library(textreadr)
library(jsonlite)
```

The data dictionary files were provided in rich text file (RTF) format. The function below allows us to read in all of the rtfs in a given directory and converts them into a single dataframe.

```{r}
read_in_rtfs <- function(directory, number_columns, columns_names, col_indices_to_remove=c(), row_indices_to_remove=c()){
  list_of_files <- list.files(directory)
  full_rtf_df <- data.frame(matrix(nrow=0, ncol=number_columns))
  colnames(full_rtf_df) <- columns_names
  for(infile in list_of_files){
    form <- str_split(infile, '\\.')[[1]][1]
    raw_rtf <- read_rtf(paste(directory, infile, sep=''))
    rtf_df <- data.frame(matrix(nrow=0, ncol=number_columns))
    for (i in 1:length(raw_rtf)) {
      parsed_line <- str_split(raw_rtf[i], '\\*\\| | \\| | \\|')[[1]]
      rtf_df <- rbind(rtf_df, parsed_line)
    }
    no_empty <- rtf_df[-row_indices_to_remove, -col_indices_to_remove]
    colnames(no_empty) <- columns_names
    clean_df <- no_empty[!apply(no_empty == "", 1, all),]
    clean_df$file_name <- form
    full_rtf_df <- rbind(full_rtf_df, clean_df)
  }
  rownames(full_rtf_df) <- NULL
  return(full_rtf_df)
}
```

```{r}
fus_i_df <- read_in_rtfs("../input/Codebooks/BABY_HUG_FUS_I_Codebook/", 
                         10, 
                         c("Variable_Label_VAR", "Variable_Name", "Category",
                           "N_percent", "N_Missing", "Mean_SD", "Median_Q1_Q3",
                           "Range_of_Values"),
                         c(1, 10),
                         c(1))
```

```{r}
fus_ii_df <- read_in_rtfs("../input/Codebooks/BABY_HUG_FUS_II_Codebook/", 
                         10, 
                         c("Variable_Label_VAR", "Variable_Name", "Category",
                           "N_percent", "N_Missing", "Mean_SD", "Median_Q1_Q3",
                           "Range_of_Values"),
                         c(1, 10),
                         c(1))
```

```{r}
# Something is going on where the empty rows are not removed. 
# Unsure what is causing it - bug fix below
phase_iii_rct_df <- read_in_rtfs("../input/Codebooks/BABY_HUG_PhaseIII_RCT_Codebook/", 
                         10, 
                         c("Variable_Label_VAR", "Variable_Name", "Category",
                           "N_percent", "N_Missing", "Mean_SD", "Median_Q1_Q3",
                           "Range_of_Values"),
                         c(1, 10),
                         c(1))
reference_row <- phase_iii_rct_df[17, -9] # Get an example of an empty row excluding the last column with the form name
inds_to_drop <- c()
for(i in 1:nrow(phase_iii_rct_df)){
  test_vec <- phase_iii_rct_df[i, -9]
  if(sum(test_vec == reference_row) == 8){
    inds_to_drop <- c(inds_to_drop, i)
  }
}
phase_iii_df <- phase_iii_rct_df[-inds_to_drop, ]
```

Though the rtfs were read into the dataframe, there were some instances of data missing. This code fills in missing data.

```{r}
#while(length(ind <- which(fus_i_df$Variable_Label_VAR == "")) > 0) {
#  fus_i_df$Variable_Label_VAR[ind] <- fus_i_df$Variable_Label_VAR[ind-1]
#}
while(length(ind <- which(fus_i_df$Variable_Name == "")) > 0) {
  fus_i_df$Variable_Name[ind] <- fus_i_df$Variable_Name[ind-1]
}
for(i in 1:nrow(fus_i_df)){
  if(i > 1) {
    if (fus_i_df[i, "Variable_Label_VAR"] == '' & fus_i_df[i, "Variable_Name"] == fus_i_df[i-1, "Variable_Name"]){
      fus_i_df[i, "Variable_Label_VAR"] <- fus_i_df[i-1, "Variable_Label_VAR"]
    }
  }
}

#while(length(ind <- which(fus_ii_df$Variable_Level_VAR == "")) > 0) {
#  fus_ii_df$Variable_Level_VAR[ind] <- fus_ii_df$Variable_Level_VAR[ind-1]
#}

while(length(ind <- which(fus_ii_df$Variable_Name == "")) > 0) {
  fus_ii_df$Variable_Name[ind] <- fus_ii_df$Variable_Name[ind-1]
}

for(i in 1:nrow(fus_ii_df)){
  if(i > 1) {
    if (fus_ii_df[i, "Variable_Label_VAR"] == '' & fus_ii_df[i, "Variable_Name"] == fus_ii_df[i-1, "Variable_Name"]){
      fus_ii_df[i, "Variable_Label_VAR"] <- fus_ii_df[i-1, "Variable_Label_VAR"]
    }
  }
}

#while(length(ind <- which(phase_iii_df$Variable_Level_VAR == "")) > 1) {
#  phase_iii_df$Variable_Level_VAR[ind] <- phase_iii_df$Variable_Level_VAR[ind-1]
#}
while(length(ind <- which((phase_iii_df$Variable_Name == reference_row$Variable_Name) | (phase_iii_df$Variable_Name == ''))) > 0) {
  phase_iii_df$Variable_Name[ind] <- phase_iii_df$Variable_Name[ind-1]
}

for(i in 1:nrow(phase_iii_df)){
  if(i > 1) {
    if ((phase_iii_df[i, "Variable_Label_VAR"] == reference_row$Variable_Label_VAR | phase_iii_df[i, "Variable_Label_VAR"] == '') & phase_iii_df[i, "Variable_Name"] == phase_iii_df[i-1, "Variable_Name"]){
      phase_iii_df[i, "Variable_Label_VAR"] <- phase_iii_df[i-1, "Variable_Label_VAR"]
    }
  }
}
```

Additionally, we have information on each variable from SAS. 
```{r}
sas_fus_i <- read.csv('../input/metadata_files/fus_i_metadata.csv')
sas_fus_ii <- read.csv('../input/metadata_files/fus_ii_metadata.csv')
sas_phase_iii <- read.csv('../input/metadata_files/phase_iii_metadata.csv')

fus_i_df <- full_join(fus_i_df, 
                  sas_fus_i %>% 
                    select(NAME, TYPE, LABEL, MEMNAME) %>%
                    mutate(MEMNAME = tolower(MEMNAME)),
                  by = c("Variable_Name" = "NAME", "file_name" = "MEMNAME"))

fus_ii_df <- full_join(fus_ii_df, 
                  sas_fus_ii %>% 
                    select(NAME, TYPE, LABEL, MEMNAME) %>%
                    mutate(MEMNAME = tolower(MEMNAME)),
                  by = c("Variable_Name" = "NAME", "file_name" = "MEMNAME"))

phase_iii_df <- full_join(phase_iii_df, 
                  sas_phase_iii %>% 
                    select(NAME, TYPE, LABEL, MEMNAME) %>%
                    mutate(MEMNAME = tolower(MEMNAME)),
                  by = c("Variable_Name" = "NAME", "file_name" = "MEMNAME"))
```

The first level of information we will save is the variable-level information.
```{r}
save_var_metadata <- function(df) {
  
  final_df <- data.frame(df %>%
                           select(Variable_Name, Variable_Label_VAR, LABEL, file_name) %>%
                           unique())
  
  rownames(final_df) <- NULL
  
  for (ind in c(1:nrow(final_df))) {
    var_df <- df %>%
      filter(Variable_Name == final_df[ind, "Variable_Name"] &
               #Variable_Label_VAR == final_df[ind, "Variable_Label_VAR"] &
               file_name == final_df[ind, "file_name"]) %>%
      select(Category, N_percent, N_Missing) 
    var_df <- data.frame(var_df)
    final_df[ind, 'metadata'][[1]] <- list(var_df)
  }
  
  return(final_df)
}
```

```{r}
second_fus_i <- save_var_metadata(fus_i_df)
second_fus_ii <- save_var_metadata(fus_ii_df)
second_phase_iii <- save_var_metadata(phase_iii_df)
```

Next let's save the variables as metadata for each of the files. 
```{r}
save_file_metadata <- function(df){
  final_df <- data.frame(df %>%
                           select(file_name) %>%
                           unique())
  
  rownames(final_df) <- NULL
  
  for (ind in c(1:nrow(final_df))){
    var_df <- df %>%
      filter(file_name == final_df[ind, "file_name"]) %>%
      select(Variable_Name, Variable_Label_VAR, LABEL, metadata) %>%
      rename(data_dict_label = Variable_Label_VAR,
             sas_label = LABEL)
    var_df <- data.frame(var_df)
    final_df[ind, 'var_data'][[1]] <- list(var_df)
  }
  return(final_df)
}
```

```{r}
third_fus_i <- save_file_metadata(second_fus_i)
third_fus_ii <- save_file_metadata(second_fus_ii)
third_phase_iii <- save_file_metadata(second_phase_iii)
```

We will next save the file-level metadata. A manually curated file with form descriptions was created.
Let's add these descriptions to the dataframe now.
```{r}
file_info <- read.csv("../intermediates/babyhug_curated_form_info.csv")
third_fus_i <- left_join(third_fus_i, 
             file_info %>% 
               filter(Study == "FUS_I") %>% 
               select(Form, Info) %>%
               mutate("form" = tolower(Form)),
             by = c("file_name" = "form"))
third_fus_ii <- left_join(third_fus_ii, 
             file_info %>% 
               filter(Study == "FUS_II") %>% 
               select(Form, Info) %>%
               mutate("form" = tolower(Form)),
             by = c("file_name" = "form"))
third_phase_iii <- left_join(third_phase_iii, 
             file_info %>% 
               filter(Study == "PHASE_III") %>% 
               select(Form, Info) %>%
               mutate("form" = tolower(Form)),
             by = c("file_name" = "form"))
```

Now we can save this information as file-level metadata for each study and combine into a single dataframe.
```{r}
save_final_level <- function(df, study_name){
  final_df <- data.frame(study_name)
  mini_df <- df %>% 
    select(file_name, Info, var_data) %>% 
    rename(file_label = Info)
  final_df[1, 'study_data'][[1]] <- list(mini_df)
  return(final_df)
}
```

```{r}
final_fus_i <- save_final_level(third_fus_i, "BABY HUG Follow-up Study I")
final_fus_ii <- save_final_level(third_fus_ii, "BABY HUG Follow-up Study II")
final_phase_iii <- save_final_level(third_phase_iii, "BABY HUG Phase III Randomized Clinical Trial")
```

```{r}
compiled <- rbind(final_fus_i, final_fus_ii, final_phase_iii)
```

Writing out to JSON.

```{r}
my_json <- toJSON(compiled, pretty=FALSE)
```


Using the `write_json` function outputs quotations with escape characters ("/"). This causes problems with the JSON file format. This can be dealt with by converting the JSON object into a string and writing this to a text file.

```{r}
test_string_json <- as.character(my_json) # Convert to character/string
fileConn <- file("../output/babyhug_metadata.json")
writeLines(test_string_json, fileConn)
close(fileConn)
# This works for writing a JSON file without the escape characters
```




Attempted to compose a more general function that can be applied to any step in this process. Though the function below works, it take a long time to complete. Generally, curation should follow this format.

```{r}
#consolidate_levels <- function(df, levels_to_keep, levels_to_collapse, metadata_col_name) {
#  groups <- data.frame(df %>% select(all_of(levels_to_keep)) %>% unique())
#  rownames(groups) <- NULL
#  
#  #final_df <- data.frame(df %>% select(all_of(levels_to_keep)) %>% unique())
#                         
#  for (ind in 1:nrow(groups)) {
#      info_vec <- groups[ind, levels_to_keep]
#      inds_to_get <- c()
#      for (df_ind in 1:nrow(df)){
#        test_vec <- df[df_ind, levels_to_keep]
#        if(sum(test_vec == info_vec) == length(levels_to_keep)) {
#          inds_to_get <- c(inds_to_get, df_ind)
#        }
#      var_df <- data.frame(df[inds_to_get, levels_to_collapse])
#      groups[ind, metadata_col_name][[1]] <- list(var_df)
#    }
#  }
#  return(groups)
#}
```
