---
title: "ORCHID Metadata curation"
author: "Emily Hughes"
date: "2/9/2022"
output: html_document
---

Libraries
```{r}
library(tidyverse)
library(jsonlite)
```

First we load the data from sas
```{r}
file_info <- read.csv("../input/ORCHID_METADATA.csv")
file_info <- file_info %>% mutate(MEMNAME = ifelse(MEMNAME == "ALLDATA", 
                                                   "alldata.csv", 
                                                   paste(tolower(MEMNAME), ".sas7bdat", sep='')),
                                  TYPE = ifelse(TYPE==1, 
                                                "continuous", 
                                                ifelse(TYPE==2, "categorical", "data missing"))) %>%
  mutate(TYPE = ifelse(is.na(TYPE), "data missing", TYPE)) %>%
  filter(!MEMNAME %in% c("alldata_dd.sas7bdat", "derived_vars_dd.sas7bdat")) %>% 
  select(MEMNAME, NAME, TYPE, LABEL) %>%
  rename(data_file_name = MEMNAME,
         variable_id = NAME,
         variable_type = TYPE,
         variable_label_from_data_file = LABEL)
```


Files
- the alldata_dd.csv file has variable descriptions
- we have additional variable descriptions in the derived_vars_dd.csv file
```{r}
alldata_dd <- read.csv('../input/alldata_dd.csv')

df <- left_join(file_info %>% select(variable_id, variable_label_from_data_file),
                  alldata_dd %>% select(name, label),
                  by = c('variable_id' = 'name'))

derived_vars <- read.csv('../input/derived_vars_dd.csv')

df2 <- left_join(df,
                 derived_vars %>% select(name, label) %>% rename('derived_var_label' = 'label'),
                 by = c('variable_id' = 'name'))

write.csv(df2, '../intermediates/annotated_dd.csv', na = '', row.names = FALSE)

```

We manually annotate the variable IDs and names based on the ORCHID Dataset Documents_V2_20NOV2020.pdf file.
We match the forms based on variable ID and save the form info in manually_annotated_dd.csv.
We do not add additional variable descriptions at this time.
```{r}
df3 <- read.csv('../intermediates/manually_annotated_dd.csv')

df4 <- df3 %>%
  mutate(variable_label_from_data_dictionary = ifelse(label == '', derived_var_label,
                                                      ifelse(label == derived_var_label, label, paste(label, derived_var_label)))) %>%
  select(-c(label, derived_var_label)) %>%
  rename(variable_description = desc) %>%
  mutate(variable_name = ifelse(variable_label_from_data_file != '', variable_label_from_data_file, variable_label_from_data_dictionary)) %>%
  left_join(file_info %>% select(variable_id, variable_type, data_file_name)) %>%
  rename(form_name = form) %>%
  mutate(study = 'ORCHID',
         study_name = 'PETAL Network: Outcomes Related to COVID-19 Treated With Hydroxychloroquine Among Inpatients With Symptomatic Disease (ORCHID) Trial',
         study_phs_number = 'phs002299',
         study_url = 'https://www.ncbi.nlm.nih.gov/projects/gap/cgi-bin/study.cgi?study_id=phs002299.v1.p1'
         )


```

## Create JSON file

Start with variable metadata
```{r}
variable_df <- df4 %>% 
  select(variable_id, variable_name, variable_type, data_file_name, form_name) %>%
  unique()

for(ind in 1:nrow(variable_df)){
  var_df <- df4 %>%
    filter(variable_id == variable_df[ind, 'variable_id'],
           variable_name == variable_df[ind, 'variable_name'],
           data_file_name == variable_df[ind, 'data_file_name']) %>%
    select(variable_label_from_data_dictionary, variable_label_from_data_file, variable_description)
  variable_df[ind, 'variable_metadata'] [[1]] <- list(var_df)
}

```

Group variables into forms
```{r}
form_df <- df4 %>% select(form_name, data_file_name) %>% unique()

for(ind in 1:nrow(form_df)){
  f_df <- variable_df %>%
    filter(variable_id == variable_df[ind, 'variable_id'],
           variable_name == variable_df[ind, 'variable_name'],
           variable_type == variable_df[ind, 'variable_type']) %>%
    select(variable_label_from_data_dictionary, variable_label_from_data_file, variable_description)
  variable_df[ind, 'variable_metadata'] [[1]] <- list(var_df)
}

```














