---
title: "DCC Harmonized Curation"
output: html_document
---

This notebook is a little different in that the goal of the JSON file is to provide the desired dataset IDs for certain variable IDs. The desired dataset IDs are determined by the PIC-SURE path and then outputted as JSON.

Libraries
```{r}
library(tidyverse)
library(pdftools)
library(jsonlite)
# Set working directory to pic-sure-metadata-curation/dcc_harmonized if necessary
```

Connect to pic-sure and pull all harmonized variables
```{r}
#system(command = 'conda install -c conda-forge r-devtools --yes')
devtools::install_github("hms-dbmi/pic-sure-r-client", ref="master", force=T, quiet=TRUE)
devtools::install_github("hms-dbmi/pic-sure-r-adapter-hpds", ref="master", force=T, quiet=TRUE)
devtools::install_github("hms-dbmi/pic-sure-biodatacatalyst-r-adapter-hpds", ref="new-search", force=T)
library(hpds)
```

```{r}
PICSURE_network_URL = "https://biodatacatalyst.integration.hms.harvard.edu/picsure"
token_file <- "../input/token.txt"
token <- scan(token_file, what = "character")
connection <- picsure::connect(PICSURE_network_URL, token)
authPicSure = bdc::use.authPicSure(connection)

```

```{r}
dictionary <- bdc::use.dictionary(connection) # set up the variable dictionary
harmonized_dic <- bdc::find.in.dictionary(dictionary, "harmonized")
harmonized_df <- bdc::extract.dataframe(harmonized_dic)
head(harmonized_df)

```

Organize data as datatable
```{r}
my_split <- function(path){
  return(strsplit(path, '\\\\')[[1]][3])
}

harmonized_df <- harmonized_df %>%
  mutate(group_id = sapply(HPDS_PATH, my_split))

raw <- harmonized_df

```


Now we will add variable-level metadata information for each variable.
```{r}
variable_df <- raw %>% 
  select(var_id, var_name, group_id) %>%
  unique()
rownames(variable_df) <- NULL

for(ind in 1:nrow(variable_df)){
  var_df <- raw %>% 
    filter(var_id == variable_df[ind, 'var_id'] &
           var_name == variable_df[ind, 'var_name'] &
           group_id == variable_df[ind, 'group_id']) %>%
    select(var_description, data_type)
  variable_df[ind, 'variable_metadata'] [[1]] <- list(var_df)
}
```

Now we will add variables to variable groups.
```{r}
vargroup_df <- variable_df %>% 
  select(group_id) %>%
  unique()
rownames(vargroup_df) <- NULL

for(ind in 1:nrow(vargroup_df)){
  vargroup <- variable_df %>%
    filter(group_id == vargroup_df[ind, 'group_id']) %>%
    select(var_id, var_name, variable_metadata)
  vargroup_df[ind, "variable"][[1]] <- list(vargroup)
}
```

Now we will add study information.
```{r}
study <- "DCC Harmonized data set"
study_name <- "DCC Harmonized data set"
study_phs_number <- "DCC Harmonized data set"
study_url <- "https://topmed.nhlbi.nih.gov/dcc-pheno"

final_df <- data.frame(study, study_name, study_phs_number, study_url)

final_df[1, 'var_groups'][[1]] <- list(vargroup_df)

my_json <- toJSON(final_df, pretty=FALSE)

```


Using the `write_json` function outputs quotations with escape characters ("/"). This causes problems with the JSON file format. This can be dealt with by converting the JSON object into a string and writing this to a text file.

```{r}
test_string_json <- as.character(my_json) # Convert to character/string
fileConn <- file("../output/dcc_harmonized.json")
writeLines(test_string_json, fileConn)
close(fileConn)

# This works for writing a JSON file without the escape characters
```