---
title: "STOP-II Metadata Curation"
author: "Emily Hughes"
date: "1/27/2022"
output: html_document
---

Install libraries
```{r}
library(tidyverse)
library(dplyr)
library(jsonlite)
```

Read in files given for STOP-II study. This includes the SAS output about each variable and a manually curated file about the forms and their descriptions.
```{r}
sas_info <- read.csv("../input/METADATA.csv")
file_info <- read.csv("../intermediates/stopii_file_info.csv")
```

Now we can combine this information and clean the dataframe to include only the information we are interested in.
```{r}
raw <- full_join(sas_info, 
                 file_info %>%
                   mutate(sas_file = toupper(sas_file)) %>%
                   rename(form_label = label),
                 by = c("MEMNAME" = "sas_file")) %>%
  select(MEMNAME, NAME, TYPE, LABEL, form, form_label) %>% 
  rename(sas_file = MEMNAME,
         var_name = NAME,
         var_type = TYPE,
         var_label = LABEL,
         form_number = form)
```

Save the variable-level data for each form
```{r}
save_var_metadata <- function(df) {
  
  final_df <- data.frame(df %>%
                           select(form_number, sas_file, form_label) %>%
                           unique())
  
  rownames(final_df) <- NULL
  
  for (ind in c(1:nrow(final_df))) {
    var_df <- df %>%
      filter(form_number == final_df[ind, "form_number"]) %>%
      select(var_name, var_label, var_type) 
    var_df <- data.frame(var_df)
    final_df[ind, 'var_data'][[1]] <- list(var_df)
  }
  
  return(final_df)
}

var_df <- save_var_metadata(raw)
```

Now we can  write out the information to JSON.
```{r}
my_json <- toJSON(var_df, pretty=FALSE)
test_string_json <- as.character(my_json) # Convert to character/string
fileConn <- file("../output/stopii_metadata.json")
writeLines(test_string_json, fileConn)
close(fileConn)
```

